Stack Safety is a Security Property

### 2021-04-16 tex/main.tex
polishing definition of stepwise confidentiality

\definition
For any call trace \(\MPCT \in \MPCT^*\) with \(\head(\MPCT) = \mach,\pol,(\domMap,\rts)\),
let \(\components\) be the set of components \(\component\) such that
\(\domMap ~ \component = \outside\). That is, at the start of some call, we take every
component in the stack.
A system enjoys \emph{stepwise stack confidentiality} if,
for all \(\nach\) such that \(\mach \approx_\components \nach\) and
\(\nach,\pol,\domMap \hookrightarrow \NPCT | \neg f_{|\rts|}\),
\(\MPCT \doteq \NPCT\)---if every variant (with the same policy state)
steps in lockstep until both traces have reached a point whose depth is
below the starting one. This is a return.

>>>>

\definition
For any call trace \(\MPCT \in \MPCT^*\) with \(\head(\MPCT) = \mach,\pol,(\domMap,\rts)\),
let \(\components\) be the set of components \(\component\) such that
\(\domMap ~ \component = \outside\).
%That is, at the start of some call, we take every component in the stack.
A system enjoys \emph{stepwise stack confidentiality} if,
for all \(\nach\) and \(\NPCT\) such that \(\mach \approx_\components \nach\)
and \(\nach,\pol,\domMap \hookrightarrow \NPCT | \neg f_{|\rts|}\),
\(\MPCT \doteq \NPCT\) holds.

%\medskip

In other words, stepwise stack confidentiality states that if we vary every component of the stack,
the resulting trace (starting in the same policy state) steps in lockstep with the
original trace until both have reached a point whose depth is below the starting
depth (this is a return).
